\documentclass[11pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=2.5cm]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue!50!black,
            urlcolor=blue!50!black}
\pagestyle{empty}
\setlength{\parskip}{0.45em}
\setlength{\parindent}{0pt}

\begin{document}

\hfill\today

\medskip

To the Editorial Board\\
\emph{Physical Review Research}

\medskip

Dear Editors,

Please consider the enclosed manuscript, ``A two-feedback
Vicsek--Couzin flock: dense-phase noise rectification as the
unifying action of density-gated motility--noise coupling,'' for
publication in Physical Review Research as an original research
article.

The standard Vicsek model fixes the self-propulsion speed and the
angular-noise distribution as global constants. Two relaxations
have been studied separately: a density-dependent speed, which
drives motility-induced phase separation, and heavy-tailed
L\'evy reorientations, which reshape the order--disorder
transition. We ask what happens when both are switched on
together, gated by a single density-dependent sigmoid in the local
neighbour count, and we isolate each contribution with a four-way
ablation (baseline / noise-shape-only / motility-only / full) run
on one code path.

We find that heavy-tailed noise on its own grows no size-dependent
susceptibility; only the motility channel builds a phase-separated
dense phase. The noise-shape channel then acts inside that dense
phase through a single route, rectifying its heavy-tailed Cauchy
kicks into Gaussian ones. What at first looks like a super-additive
cooperation between the two channels we show, with a matched-noise
control, to be one effect: equalising the effective dense
decorrelation collapses the susceptibility excess ($\Delta_9$ from
$+0.45$ to $+0.02$) and reverses the static $g(r)$ and dynamic
$C(\tau)$ gaps, so the two channels are additive and the noise-shape
feedback simply lowers the dense effective noise. The robust
results are a clean two-regime split that reproduces across three
densities, a density-gated L\'evy-to-Gaussian conversion of
dense-phase turning, and a decoupled-sigmoid dissection that pins
the motility threshold as the sole control variable and shows the
effect to be a property of the metric kernel.

We believe the work suits Physical Review Research well. It is a
careful, well-controlled study of an active-matter model (Vicsek
and Couzin flocking, motility-induced phase separation, giant
number fluctuations, finite-size scaling of the order--disorder
transition, and density-stratified correlation functions) whose
central result is a clarifying, rigorously controlled one. The
journal's broad, open-access remit and its receptiveness to solid
unifying and negative results make it a natural home, and the work
should interest the active-matter, soft-matter and non-equilibrium
statistical-physics communities the journal serves.

The analysis is deliberately conservative. Claims rest on
ten-seed finite-size scans with seed-bootstrap confidence
intervals and non-parametric (Wilcoxon signed-rank,
Mann--Whitney) tests rather than Gaussian $z$-scores; null results
(a passive noise-shape threshold, negligible hysteresis, no
extended patch lifetime, a topological-kernel breakdown, and a
falsified mean-density prediction) are reported rather than buried;
the finite-size slopes are presented as crossover rates, not
asymptotic exponents, dropping as the lever is extended to nine
sizes ($L$ up to $256$); and the apparent synergy is shown, by the
matched-noise control, to be additive at matched noise rather than
an emergent cooperation. All code and data are openly available at
\url{https://github.com/yayayou47/two-feedback-vicsek} for
bit-for-bit reproduction of every figure.

This manuscript is original, has not been published previously,
and is not under consideration at any other journal. Its two
authors declare no competing interests. One
supplementary-material PDF accompanies the submission. As
potential referees, we would suggest specialists in active-matter
and flocking models, in finite-size scaling of non-equilibrium
phase transitions, and in motility-induced phase separation.

Thank you for considering our submission.

\medskip

Sincerely,\\[0.8em]
Yaya Youssouf Yaya\\
\emph{Corresponding author, on behalf of both authors}\\
D\'epartement de Math\'ematiques, \'Ecole Normale Sup\'erieure de
N'Djam\'ena, Tchad\\
Chercheur Associ\'e, LMA, Universit\'e Assane Seck de Ziguinchor,
S\'en\'egal\\
\texttt{yy.y@zig.univ.sn} \;\; ORCID:
\href{https://orcid.org/0000-0003-0781-4923}{0000-0003-0781-4923}

\end{document}
