\documentclass[11pt,a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[margin=2.5cm]{geometry}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue!50!black,
            urlcolor=blue!50!black}
\pagestyle{empty}
\setlength{\parskip}{0.45em}
\setlength{\parindent}{0pt}

\begin{document}

\hfill\today

\medskip

To the Editorial Board\\
\emph{Journal of Statistical Mechanics: Theory and Experiment} (JSTAT)

\medskip

Dear Editors,

Please consider the enclosed manuscript, ``A two-feedback
Vicsek--Couzin flock: density-stratified heading correlations as
the robust fingerprint of motility--noise coupling,'' for
publication in JSTAT as an original research article.

The standard Vicsek model fixes the self-propulsion speed and the
angular-noise distribution as global constants. Two relaxations
have been studied separately: a density-dependent speed, which
drives motility-induced phase separation, and heavy-tailed
L\'evy reorientations, which reshape the order--disorder
transition. We ask what happens when both are switched on
together, gated by a single density-dependent sigmoid in the local
neighbour count, and we isolate each contribution with a four-way
ablation (baseline / noise-shape-only / motility-only / full) run
on one code path.

We find that heavy-tailed noise on its own grows no size-dependent
susceptibility; only the motility channel builds a phase-separated
dense phase, on top of which the otherwise-silent noise-shape
adaptation adds a finite-size super-additive excess. The robust,
scale-spanning fingerprint of the coupling is microscopic: a
density-stratified dense-phase heading correlation $g(r)$ and its
dynamic counterpart $C(\tau)$, together with a single-particle
switch of dense-phase reorientation from L\'evy-like to Gaussian
(per-step turning-angle distribution and density-stratified mean
squared displacement). A decoupled-sigmoid sweep identifies the
motility threshold as the sole control variable, and a
hydrodynamic appendix supplies the analytic counterpart.

We believe the work fits JSTAT squarely. It is a
statistical-mechanics study of an active-matter model --- Vicsek
and Couzin flocking, motility-induced phase separation, giant
number fluctuations, finite-size scaling of the order--disorder
transition, and density-stratified correlation functions --- and
should interest the active-matter and non-equilibrium
statistical-mechanics communities the journal serves.

The analysis is deliberately conservative. Claims rest on
ten-seed finite-size scans with seed-bootstrap confidence
intervals and non-parametric (Wilcoxon signed-rank,
Mann--Whitney) tests rather than Gaussian $z$-scores; null results
(a passive noise-shape threshold, negligible hysteresis, no
extended patch lifetime, a topological-kernel breakdown) are
reported rather than buried; and the macroscopic finite-size
synergy is presented as a finite-size effect, not an asymptotic
critical exponent. All code and data are openly available at
\url{https://github.com/yayayou47/two-feedback-vicsek} for
bit-for-bit reproduction of every figure.

This manuscript is original, has not been published previously,
and is not under consideration at any other journal. It has a
single author, who declares no competing interests. One
supplementary-material PDF accompanies the submission. As
potential referees, we would suggest specialists in active-matter
and flocking models, in finite-size scaling of non-equilibrium
phase transitions, and in motility-induced phase separation.

Thank you for considering our submission.

\medskip

Sincerely,\\[0.8em]
Yaya Youssouf Yaya\\
D\'epartement de Math\'ematiques, \'Ecole Normale Sup\'erieure de
N'Djam\'ena, Tchad\\
Chercheur Associ\'e, LMA, Universit\'e Assane Seck de Ziguinchor,
S\'en\'egal\\
\texttt{yy.y@zig.univ.sn} \;\; ORCID:
\href{https://orcid.org/0000-0003-0781-4923}{0000-0003-0781-4923}

\end{document}
